### 2021-04-23 sections/model_overview/main.tex
Add reference for normal form games
Add diagram of the queueing model
Added the diagram for the queueing model and some text to
accompany it. There were also minor changes to some of the
prewritten text.

\begin{itemize}
    \item The decision makers of two queueing systems;
    \item a service that distributes individuals to these two queueing systems.
\end{itemize}

his is a standard Normal form game~\cite{},  
% TODO: Cite a Game Theory text book (Maschler et al. would do)
in that each player in this game has their own objectives which they aim to 
optimise.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.   
% TODO: Depending on how this is described earlier, we might need a little more 
% here (as to what we mean by "blocked")

The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that the distributor allocates to them and 
other individuals from other sources. 
Each queueing system may then choose to block the individuals that arrive from 
the distributor when the system reaches a certain capacity. 
The strategy sets for each queueing system is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of the two queueing systems. We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.
Their choice of strategy will then rely solely on satisfying their own 
objective, which is to make sure that the waiting time of a proportion of 
individuals will be below the predefined target time.

This is shown diagrammatically in Figure %~ref{fig:diagram_of_queueing_system}.
% TODO: Draw diagram of queueing system
% This should include the parameters
% and clearly show the decision variable.
% Note: only do this for a single queueing system.

@@

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
individuals it sends to the first queueing system (the proportion \(1 - q\) is 
sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals.
% TODO: Clarify above (somewhere near the diagram of the queueing system) that 
% individuals can be lost at all.
Equation \ref{eq:obj-distributor} can be used to capture a mixture 
between the two objectives.

@@

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](HA){\(H_A\)};
        \node[anchor=north](HA_d1) at (3, 2){.};
        \node[anchor=north](HA_d2) at (3, -2){.};

>>>>

\begin{itemize}
    \item the decision makers of two queueing systems;
    \item a service that distributes individuals to these two queueing systems.
\end{itemize}

This is a standard Normal form game~\cite{Maschler2013},  
in that each player in this game has their own objectives which they aim to 
optimise.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.   
% TODO: Depending on how this is described earlier, we might need a little more 
% here (as to what we mean by "blocked")

The queueing systems are designed in such a way where they can accept two types
of individuals. 
These are the individuals that the distributor allocates to them and 
other individuals from other sources. 
Each queueing system may then choose to block the individuals that arrive from 
the distributor when the system reaches a certain capacity. 
The strategy sets for each queueing system is the set 
\( \{T \in \mathbb{N} \;|\; 1 \leq T \leq N\} \) where \(N \in\{N_A, N_B\}\) are 
the total capacities of the two queueing systems. We denote the chosen actions 
from the strategy set as \(T_A, T_B\) and call these \textit{threshold}s.

Both queueing systems follow a queueing model that has two waiting spaces for 
individuals. 
The first waiting zone is where the individuals queue right before receiving 
their service and has a capacity of \( N - C \), where \(N\) is the total 
capacity of the waiting space and \(C\) is the number of servers. 
The second waiting zone is where the individuals, that are sent from the 
distributor, remain until they are allowed to enter the first waiting zone.
The second waiting zone has a capacity of \(M\) and no servers.

This is shown diagrammatically in Figure ~\ref{fig:diagram_of_queueing_system}.

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % the vertical lines in Queue 1
        \foreach \i in {1,...,4, 5.7}
        \draw (2cm-\i*10pt,0) -- +(0,-1.5cm);

        % the circle in Queue 1
        \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the very start of Queue 2 
        \draw (7cm-55pt,1.1) -- +(0,-1.2cm);
        \draw (7cm-53pt,1) -- +(0,-1cm);
        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};

        % the circle in Queue 2
        \draw (7.75,0.5) circle [radius=0.75cm] node {\(C\)};

        % Arrow line from Queue 2 outside
        \draw[->] (8.5,0.525) -- +(20pt,0);

        % Line from lambda_2 to Queue 1
        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
        % First line (horizontal) after Queue 1
        \draw[-] (3.5,-0.75) -- +(20pt,0);
        % Second line (vertical) after Queue 1
        \draw (4.2, 0.525) -- (4.2, -0.75);

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{Queueing Model}
    \label{fig:diagram_of_queueing_system}
\end{figure}

Note here that both types of individuals can become lost to the system. 
Individual allocated from the distributor become lost to the system whenever 
an arrival occurs and the second waiting zone is at full capacity (\(M\) 
individuals already waiting).
Similarly, other individuals get lost whenever they arrive at the first waiting 
zone and it is at full capacity (\(N - C\) individuals already waiting).

Following this queuing model, the two queueing systems' choice of strategy will 
then rely solely on satisfying their own 
objective, which is to make sure that the waiting time in the first waiting zone 
of a proportion of individuals will be below the predefined target time.

@@

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
individuals it sends to the first queueing system (the proportion \(1 - q\) is 
sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals.
Equation \ref{eq:obj-distributor} can be used to capture a mixture 
between the two objectives.

@@

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](HA){\(H_A\)};
        \node[anchor=north](HA_d1) at (3, 2){.};
        \node[anchor=north](HA_d2) at (3, -2){.};
